Evaluating computational methods for modeling off-normal operation of gas centrifuge cascades

### 2018-07-05 abstract.tex
PPH comments 2

The goal of this work focuses on developing the necessary understanding of
potential misuse of enrichment cascades. The latter would allow more effective
international safeguards designs and approaches.  While it is straightforward to
design an enrichment cascade under ideal conditions as a function of the
theoretical feed, product and tails assays, it is very difficult to find
reliable information about the behavior of a given cascade when the feed assay
does not match the design value. Several methods have been developed to assess
the behavior of an enrichment cascade in such circumstances. In addition of the
cut ($\theta$) those methods evaluate the feed to product, feed to tails and the
product to tails enrichment ratio, respectively, $\alpha$, $\beta$ and $\gamma$,
as a function of the cascade feed assay. As those four parameters depend on each
other, determining two of them fully defines the other.  The first approach
consists of fixing $\theta$ and $\alpha$ recomputing the corresponding assays at
each stages of the cascade. The second one maintains the ideal condition of the
cascade ($\alpha$ and $\beta$ fixed across the whole cascade), modifying
$\theta$ value at each stage accordingly. Both approaches have been implemented
into the Cyclus fuel cycle simulator\cite{cyclus, mbmore.2018}. The third fixes
$\theta$ and $\gamma$, using both $\alpha$ and $\beta$ at each stage as free
parameters. The third method has been investigated in \cite{walker.2017}.

>>>>

The goal of this work focuses on developing the necessary understanding of
potential misuse of enrichment cascades, contributing to more effective
international safeguards designs and approaches.  While it is straightforward to
design an enrichment cascade under ideal conditions as a function of the
theoretical feed, product and tails assays, it is very difficult to find
reliable information about the behavior of a given cascade when the feed assay
does not match the design value. Several methods have been developed to assess
the behavior of an enrichment cascade in such circumstances. In addition to the
cut ($\theta$) those methods evaluate the feed to product, feed to tails and the
product to tails enrichment ratio, respectively, $\alpha$, $\beta$ and $\gamma$,
as a function of the cascade feed assay. As those four parameters depend on each
other, determining two of them fully defines the other.  The first approach
consists of fixing $\theta$ and $\alpha$ recomputing the corresponding assays at
each stages of the cascade. The second one maintains the ideal condition of the
cascade ($\alpha$ and $\beta$ fixed across the whole cascade), modifying
$\theta$ value at each stage accordingly. Both approaches have been implemented
into the Cyclus fuel cycle simulator\cite{cyclus, mbmore.2018}. The third fixes
$\theta$ and $\gamma$, using both $\alpha$ and $\beta$ at each stage as free
parameters. The third method has been investigated in \cite{walker.2017}.

### 2018-07-05 dis_clusion.tex
PPH comments 2

We can observe that when the cascade is left completely untouched (Model A) or
when it is slightly retuned to maintain the tails to product enrichment factor
as well as the cut of each centrifuges (Model C), chaining the cascade we can
observe high increase of the enrichment at each level.  On the contrary, when
retuning the cut of each centrifuges to maintain the ideal state of the cascades
(Model B) while chaining them, the \gls{HEU} production rate is favored over the
enrichment gain.

The tails recycling allows each model to achieve a large gain in productivity,
even for then model B in which the number of levels required to reach $90w\%$ of
$^{235}$U in the uranium does not change. Even if no cascade chaining options
achieves the same production rate as direct enrichment, the model B with tail
recycling reached about $80\%$ of the optimum production rate. Such production
rate would allow the build up of a Significant Quantity of \gls{HEU} in less
than 8 months\ldots

\section{Conclusion and future works}

This works has investigated and quantify the difference between potential
retuning of a gaseous enrichment cascade in order to chain them to produce
\gls{HEU} initially tuned to produce uranium enrichment for commercial reactors.
One of this tuning method allows up to $80\%$ of the production rate of a single
large enrichment cascade designed specifically for \gls{HEU} production using
the same number of centrifuges.

This works will be extended to the near future with additional misuse method,
allowing for example the reconfiguration of the centrifuges in the cascades.

For this study, the usage of the Cyclus fuel cycle simulator was not really
required, it only allows a quick determination of the blending equilibrium. It
is planned to make use of the Cyclus Dynamical Resource Exchange full capability
in order to automatically assign the different cascades to the different level
as function of the resources availability, optimising the productions rates in
each cases.

While mathematically correct, the authors do not guaranty the feasibility
different misuse tuning methods implemented and are welcoming any insight on the
matter.

>>>>

We can observe that when the cascade is left completely untouched (Model A) or
when it is slightly retuned to maintain the tails to product enrichment factor
as well as the cut of each centrifuges (Model C), chaining the cascade can
achieve large increase of the enrichment at each level.  On the contrary, when
retuning the cut of each centrifuges to maintain the ideal state of the cascades
(Model B) while chaining them, the \gls{HEU} production rate is favored over the
enrichment gain.

The tails recycling allows each model to achieve a large gain in productivity,
even for then model B in which the number of levels required to reach $90w\%$ of
$^{235}$U in the uranium does not change. Even if no cascade chaining options
achieves the same production rate as direct enrichment, the model B with tail
recycling reached about $80\%$ of the optimum production rate. Such production
rate would allow the accumulation of a Significant Quantity of \gls{HEU} in less
than 8 months\ldots

\section{Conclusion and futur work}

This work has investigated and quantified the difference between potential
models for retuning of a centrifuge enrichment cascade in order to chain them to produce
\gls{HEU} initially tuned to produce uranium enrichment for commercial reactors.
One of these tuning method achieves up to $80\%$ of the production rate of a single
large enrichment cascade designed specifically for \gls{HEU} production using
the same number of centrifuges.

This work will be extended to the near future with additional misuse methods,
allowing for example, the reconfiguration of the centrifuges in the cascades.

For this study, the use of the Cyclus fuel cycle simulator was not
required, it only allows a quick determination of the blending equilibrium. It
is planned to make use of the full capability of Cyclus Dynamical Resource Exchange 
in order to automatically assign the different cascades to the different level
as function of the resources availability, optimising the productions rates in
each cases.

While mathematically correct, the authors do not guaranty the feasibility of the
different misuse tuning methods implemented and are welcoming any insight on the
matter.

### 2018-07-05 experiement.tex
PPH comments 2

\section{The experiment}
This works focuses on comparing the different misuse models to a reference
calculation in which a single large cascade is build and designed to directly
produce \gls{HEU} from natural uranium.
This works uses the Cyclus fuel cycle simulator to allow material exchange
between facilities. The enrichment cascade algorithm have been implemented in
the $mbmore$ package \cite{mbmore.2018}.
In each cases, 5060 centrifuges have been used and spread across up to 30
different gas enrichment cascades.

@@

Cascade Design &       & Reference   & Default    \\
\midrule
Targeted  & Feed       & $0.71w\%$   & $0.71w\%$  \\
Assays    & Product    & $90w\%$     & $3.5w\%$   \\
          & Tails      & $0.3w\%$   & $0.3w\%$   \\
\midrule
Effective & Product    & $90.35w\%$  & $4.13w\%$  \\
Assays    & Tails      & $0.29w\%$   & $0.29w\%$  \\ 
\midrule
Stages    & Enriching  & 4          & 4          \\
Number    & Stripping  & 39         & 10         \\
\bottomrule
\end{tabular}
  \label{tab:cascade_config}
\end{table}

\subsection{Scenarios}
In the following, cascades can be connected in tandem, where each set of cascade
in parallel is called a ``level``, as illustrated in Figure
\ref{fig:cascade_level}.
Seven different simulations have been simulated, to evaluate the effectiveness
of an enrichment cascade when used outside of its designed scope :
\begin{itemize}
\item one as the reference calculation, with a single cascade designed to
    directly produce \gls{HEU} from natural uranium,
\item three calculations (one per misuse model) where default cascade are
    chained to produce \gls{HEU}, without recycling the tails of each cascade
    sending their tails to the waste,
\item three calculations (one per misuse model) where default cascade are
    chained to produce \gls{HEU}, and the tails of each cascade are recycled, blending
    the tails of one level in the feed of the previous level of
    cascades (see Figure \ref{fig:cascade_level}).
\end{itemize}

@@

\subsection{Level population}
In order to assign the optimum number of cascades to each level, a virtual cut as
been computed as:
\begin{equation}
    \theta^{v}_{j} = \frac{F_{j}-N''_{j}}{N'_{j}-N''_{j}},
\end{equation}
where, $j$ represents a level of cascade and $N_{j}$, $N'_{j}$ and $N''_{j}$
the feed, product and tails assay, respectively, of the cascades at this level.

@@

As it is not possible to assign a fraction of an enrichment cascade, cascade per
level are rounded up for each level but the first one. The remaining available
cascades is attributed to the first level.

\subsection{Timestep effect}

The different cascade levels required up to $2n+1$ timesteps
before it starts to enrich uranium, where $n$ corresponds to the level number.
This corresponds to the number of timesteps required for the material to
propagate from the natural uranium source to the $n$-th level, regardless of the
duration of the timestep (hour, day, month, etc.). This is also true for the
number of timesteps required to reach the equilibrium assays value in the tails
reprocessing cases.  As timestep can be artificially small or large, one will
only be considering equilibrium values of flow rates and assays in the following
analysis.

>>>>

\section{The experiment}
This work focuses on comparing the different misuse models to a reference
calculation in which a single large cascade is build and designed to directly
produce \gls{HEU} from natural uranium.
This works uses the Cyclus fuel cycle simulator to allow material exchange
between facilities. The enrichment cascade algorithm have been implemented in
the $mbmore$ package \cite{mbmore.2018}.
In each cases, 5060 centrifuges have been used and spread across up to 30
different gas centrifuge enrichment cascades.

@@

Cascade Design &       & Reference   & Default    \\
\midrule
Targeted  & Feed       & $0.71w\%$   & $0.71w\%$  \\
Assays    & Product    & $90w\%$     & $3.5w\%$   \\
          & Tails      & $0.3w\%$   & $0.3w\%$   \\
\midrule
Effective & Product    & $90.35w\%$  & $4.13w\%$  \\
Assays    & Tails      & $0.29w\%$   & $0.29w\%$  \\ 
\midrule
Stages    & Stripping  & 4          & 4          \\
Number    & Enriching  & 39         & 10         \\
\bottomrule
\end{tabular}
  \label{tab:cascade_config}
\end{table}

\subsection{Scenarios}
In the following, cascades can be connected in tandem, where each set of cascade
in parallel is called a ``level``, as illustrated in Figure
\ref{fig:cascade_level}.
The reseults from seven different simulations have been compared, to evaluate the effectiveness
of an enrichment cascade when used outside of its designed scope :
\begin{itemize}
\item one as the reference calculation, with a single cascade designed to
    directly produce \gls{HEU} from natural uranium,
\item three calculations (one per misuse model) where default cascade are
    chained to produce \gls{HEU}, without recycling the tails of each cascade
    sending their tails to the waste,
\item three calculations (one per misuse model) where default cascade are
    chained to produce \gls{HEU}, and the tails of each cascade are recycled, blending
    the tails of one level in the feed of the previous level of
    cascades (see Figure \ref{fig:cascade_level}).
\end{itemize}

@@

\subsection{Level population}
In order to assign the optimum number of cascades to each level, a ``level cut'' as
been computed as:
\begin{equation}
    \Omega_{j} = \frac{N_{j}-N''_{j}}{N'_{j}-N''_{j}},
\end{equation}
where, $j$ represents a level of cascade and $N_{j}$, $N'_{j}$ and $N''_{j}$
the feed, product and tails assay, respectively, of the cascades at this level.

@@

As it is not possible to assign a fraction of an enrichment cascade, cascade per
level are rounded up for each level but the first one. The remaining available
cascades are attributed to the first level.

%% \subsection{Timestep effect}
%% 
%% The different cascade levels required up to $2n+1$ timesteps
%% before it starts to enrich uranium, where $n$ corresponds to the level number.
%% This corresponds to the number of timesteps required for the material to
%% propagate from the natural uranium source to the $n$-th level, regardless of the
%% duration of the timestep (hour, day, month, etc.). This is also true for the
%% number of timesteps required to reach the equilibrium assays value in the tails
%% reprocessing cases.  As timestep can be artificially small or large, one will
%% only be considering equilibrium values of flow rates and assays in the following
%% analysis.

### 2018-07-05 results.tex
PPH comments 2

Model       &        &           & A/NR      & A/R       & B/NR      & B/R      & C/NR       & C/R          \\
%Recycling   &        &           & No        & yes       & No        & Yes     & No        & yes        \\
\midrule                                                                                                 
        &            & Feed      & $0.71w\%$ & $1.3w\%$  & $0.71w\%$ & $0.94w\%$ & $0.71w\%$ & $1.33w\%$ \\
Level 0 & Assay      & Product   & $4.13w\%$ & $7.7w\%$  & $4.13w\%$ & $5.43w\%$ & $4.13w\%$ & $4.82w\%$ \\
        &            & Tails     & $0.29w\%$ & $0.5w\%$  & $0.29w\%$ & $0.39w\%$ & $0.29w\%$ & $0.55w\%$ \\
        & Cascades   &           & 25        & 25        & 25        & 24        & 25        & 25        \\
\midrule                                                                                                 
        &            & Feed      & $4.13w\%$ & $11.9w\%$ & $4.13w\%$ & $6.84w\%$ & $4.13w\%$ & $12.2w\%$ \\
Level 1 & Assay      & Product   & $22.8w\%$ & $55.7w\%$ & $20.6w\%$ & $30.7w\%$ & $22.9w\%$ & $58.5w\%$ \\
        &            & Tails     & $1.8w\%$  & $6.6w\%$  & $1.72w\%$ & $2.91w\%$ & $1.81w\%$ & $6.52w\%$ \\
        & Cascades   &           & 3         & 4         & 3         & 4         & 3         & 4         \\
\midrule                                                                                                 
        &            & Feed      & $22.8w\%$ & $55.7w\%$ & $20.6w\%$ & $34.3w\%$ & $22.9w\%$ & $58.5w\%$ \\
Level 2 & Assay      & Product   & $78.5w\%$ & $95.0w\%$ & $61.0w\%$ & $75.8w\%$ & $82.0w\%$ & $97.0w\%$ \\
        &            & Tails     & $4.13w\%$ & $50.9w\%$ & $9.56w\%$ & $17.5w\%$ & $15.7w\%$ & $53.8w\%$ \\
        & Cascades   &           & 1         & 1         & 1         & 1         & 1         & 1         \\
\midrule                                                                                                 
        &            & Feed      & $78.5w\%$ & N.A.      & $61.0w\%$ & $75.8w\%$ & $82.3w\%$ & N.A.      \\
Level 3 & Assay      & Product   & $98.2w\%$ & N.A.      & $90.4w\%$ & $95.0w\%$ & $99.1w\%$ & N.A.      \\
        &            & Tails     & $76.1w\%$ & N.A.      & $79.3w\%$ & $56.1w\%$ & $80.3w\%$ & N.A.      \\
        & Cascades   &           & 1         & N.A.      & 1         & 1         & 1         & N.A.      \\
\bottomrule
\end{tabular}
  \label{tab:level}
\end{table}

As illustrated in Figures \ref{fig:assays} and summarized on Tab
\ref{tab:level}, the different model don't have the same effect on the cascade
behavior. While the models A and C, allow a quick enrichment gain, with the
cascades chaining, respectively 4/23/78/98 and 4/23/82/99, the model B, the
enrichment gain is only 4/21/61/90.

\begin{figure}[h!]
    \centering
    \begin{subfigure}[t]{0.45\textwidth}
        \centering
        \includegraphics[scale=0.2]{feed_assays}
        \caption{Feed Assays.}
        \label{sfig:feed_assay}
    \end{subfigure}%
    \begin{subfigure}[t]{0.45\textwidth}
        \centering
        \includegraphics[scale=0.2]{product_assays}
        \caption{Product Assays.}
        \label{sfig:product_assay}
    \end{subfigure}
    \begin{subfigure}[t]{0.45\textwidth}
        \centering
        \includegraphics[scale=0.2]{tails_assays}
        \caption{Tails Assays.}
        \label{sfig:tails_assay}
    \end{subfigure}
    \caption{Feed (\subref{sfig:feed_assay}), product
        (\subref{sfig:product_assay}) and tails assays (\subref{sfig:tails_assay})
        in $m\%$ of $^{235}$U, per cascade level from 0 to 3 (red, green, orange,
        blue), per model (A/B/C) and without/with tails recycling (NR/R).}
    \label{fig:assays}
\end{figure}

@@

\subsection{\gls{HEU} Production}

>>>>

Model       &        &            & A/NR      & A/R       & B/NR      & B/R      & C/NR       & C/R       \\
%Recycling   &        &           & No        & yes       & No        & Yes     & No        & yes        \\
\midrule                                                                                                 
        &            & Feed       & $0.71w\%$ & $1.3w\%$  & $0.71w\%$ & $0.94w\%$ & $0.71w\%$ & $1.33w\%$ \\
Level 0 & Assay      & Product    & $4.13w\%$ & $7.7w\%$  & $4.13w\%$ & $5.43w\%$ & $4.13w\%$ & $4.82w\%$ \\
        &            & Tails      & $0.29w\%$ & $0.5w\%$  & $0.29w\%$ & $0.39w\%$ & $0.29w\%$ & $0.55w\%$ \\
        & Cascades   & Real(Ideal)& 25(26.7)  & 25(26.4)  & 25(26.6)  & 24(25.8)  & 25(26.7)  & 25(26.4)  \\
\midrule                                                                                                 
        &            & Feed       & $4.13w\%$ & $11.9w\%$ & $4.13w\%$ & $6.84w\%$ & $4.13w\%$ & $12.2w\%$ \\
Level 1 & Assay      & Product    & $22.8w\%$ & $55.7w\%$ & $20.6w\%$ & $30.7w\%$ & $22.9w\%$ & $58.5w\%$ \\
        &            & Tails      & $1.8w\%$  & $6.6w\%$  & $1.72w\%$ & $2.91w\%$ & $1.81w\%$ & $6.52w\%$ \\
        & Cascades   & Real(Ideal)& 3(2.9)    & 4(3.2)    & 3(2.9)    & 4(3.4)    & 3(2.9)    & 4(3.2)    \\
\midrule                                                                                                 
        &            & Feed       & $22.8w\%$ & $55.7w\%$ & $20.6w\%$ & $34.3w\%$ & $22.9w\%$ & $58.5w\%$ \\
Level 2 & Assay      & Product    & $78.5w\%$ & $95.0w\%$ & $61.0w\%$ & $75.8w\%$ & $82.0w\%$ & $97.0w\%$ \\
        &            & Tails      & $4.13w\%$ & $50.9w\%$ & $9.56w\%$ & $17.5w\%$ & $15.7w\%$ & $53.8w\%$ \\
        & Cascades   & Real(Ideal)& 1(0.3)    & 1(0.3)    & 1(0.4)    & 1(0.6)    & 1(0.3)    & 1(0.35)   \\
\midrule                                                                                                 
        &            & Feed       & $78.5w\%$ & N.A.      & $61.0w\%$ & $75.8w\%$ & $82.3w\%$ & N.A.      \\
Level 3 & Assay      & Product    & $98.2w\%$ & N.A.      & $90.4w\%$ & $95.0w\%$ & $99.1w\%$ & N.A.      \\
        &            & Tails      & $76.1w\%$ & N.A.      & $79.3w\%$ & $56.1w\%$ & $80.3w\%$ & N.A.      \\
        & Cascades   & Real(Ideal)& 1(0.03)   & N.A.      & 1(0.08)   & 1(0.2)    & 1(0.03)   & N.A.      \\
\bottomrule
\end{tabular}
  \label{tab:level}
\end{table}

As illustrated in Figures \ref{fig:assays} and summarized on Tab
\ref{tab:level}, the different model don't have the same effect on the cascade
behavior. While the models A and C, achieve a quick enrichment gain, with the
cascades chaining, 4/23/78/98 and 4/23/82/99 respectively, model B, only
achieves an enrichment gain of 4/21/61/90.

\begin{figure}[h!]
    \centering
    \begin{subfigure}[t]{0.45\textwidth}
        \centering
        \includegraphics[scale=0.2]{feed_assays}
        \caption{Feed Assays.}
        \label{sfig:feed_assay}
    \end{subfigure}%
    \begin{subfigure}[t]{0.45\textwidth}
        \centering
        \includegraphics[scale=0.2]{product_assays}
        \caption{Product Assays.}
        \label{sfig:product_assay}
    \end{subfigure}
    \begin{subfigure}[t]{0.45\textwidth}
        \centering
        \includegraphics[scale=0.2]{tails_assays}
        \caption{Tails Assays.}
        \label{sfig:tails_assay}
    \end{subfigure}
    \caption{Feed (\subref{sfig:feed_assay}), product
        (\subref{sfig:product_assay}) and tails assays (\subref{sfig:tails_assay})
        in $w\%$ of $^{235}$U, per cascade level from 0 to 3 (red, green, orange,
        blue), per model (A/B/C) and without/with tails recycling (NR/R). The
        black dashed line represents the $90 w\%$ enrichment threshold.}
    \label{fig:assays}
\end{figure}

@@

\subsection{\gls{HEU} Production Rate}

### 2018-07-05 theory.tex
PPH comments 2

The cascade is built as an ideal cascade, with no losses in the separative work,
which corresponds to $\alpha =\beta = const$ for all stages of the cascade, where
$\alpha$ and $\beta$ respectively represent the feed to product and the feed to
tails enrichment factors.  $\alpha$ and $\beta$ can be expressed as function of
the abundance ($R$) or the enrichment ($N$) of respectively the product
($R'$, $N'$) and the feed ($R$, $N$) and the feed and the tails ($R''$, $N''$) such
as:
\begin{subequations} \label{eq:alphabeta}
    \begin{equation} \label{eq:alpha_def}
        \alpha = \frac{R'}{R} = \frac{N'}{1-N'}\frac{1-N}{N} 
\end{equation}
\\
\begin{equation}\label{eq:beta-def}
        \beta = \frac{R}{R''} = \frac{N}{1-N}\frac{1-N''}{N''} 
\end{equation}
\end{subequations}

@@

\begin{equation}
\setcounter{MaxMatrixCols}{20}
\begin{bmatrix}
     -1        & 1-\theta_{_{S+1}} & 0 & ...  & 0              & 0              & 0                 & 0                 & 0                 & ...  & 0               & 0 \\
 \theta_{_{S}} & -1                & 0 & ...  & 0              & 0              & 0                 & 0                 & 0                 & ...  & 0               & 0 \\
               &                   &   &     &                &                & ...               &                   &                   &     &                 &   \\
 0             & 0                 & 0 & ...  & \theta_{_{-2}} & -1             & 1 - \theta_{_{0}} & 0                 & 0                 & ...  & 0               & 0 \\
 0             & 0                 & 0 & ...  & 0              & \theta_{_{-1}} & -1                & 1 - \theta_{_{1}} & 0                 & ...  & 0               & 0 \\
 0             & 0                 & 0 & ...  & 0              & 0              & \theta_{_{0}}     & -1                & 1 - \theta_{_{2}} & 0   & ...             & 0 \\
               &                   &   &     &                &                & ...               &                   &                   &     &                 &   \\
 0             & 0                 & 0 & ...  & 0              & 0              & 0                 & 0                 & 0                 & ...  & -1              & 1-\theta_{_{E}} \\
 0             & 0                 & 0 & ...  & 0              & 0              & 0                 & 0                 & 0                 & ...  & \theta_{_{E-1}} & -1
 \end{bmatrix}
 \times
 \begin{bmatrix}
     F_{_{S}}   \\
     F_{_{S+1}} \\
     \cdots     \\
     F_{_{-1}}  \\
     F_{_{0} }  \\
     F_{_{1} }  \\
     \cdots     \\
     F_{_{E-1}} \\
     F_{_{E}}
 \end{bmatrix}
 =
 \begin{bmatrix}
     0      \\
     0      \\
     \cdots \\
     0      \\
     F      \\
     0      \\
     \cdots \\
     0      \\
     0
\end{bmatrix}
%\caption{caption needed!}
\label{eq:flow}
\end{equation}

@@

Little information is available about optimising an existing enrichment cascade
that is being fed with a feed enrichment that does not match the design one. So
far 3 different methods have been investigated.

The first one assumes that no change are been made on the cascade, i.e $\delta
U$, $F$ and $\theta$ are fixed across all stages. The second one assumes the cut
value at each stage is retuned to maintain the ideal state of the cascade,
$\alpha$ and $\beta$ remain fixed. The last one, described in \cite{walker.2017}
assumes the tails to product enriching factor and the cut remain constants ($\gamma =
\alpha\times\beta$). Models behaviors and assumptions are summarized in Tab.
\ref{tab:models}.

>>>>

The cascade is built as an ideal cascade, with no losses in the separative work,
which corresponds to $\alpha =\beta = const$ for all stages of the cascade, where
$\alpha$ and $\beta$ represent the feed to product and the feed to
tails enrichment factors respectively.  $\alpha$ and $\beta$ can be expressed as function of
the abundance ($R$) or the enrichment ($N$) of respectively the product
($R'$, $N'$) and the feed ($R$, $N$) and the feed and the tails ($R''$, $N''$) such
as:
\begin{subequations} \label{eq:alphabeta}
    \begin{equation} \label{eq:alpha_def}
        \alpha = \frac{R'}{R} = \frac{N'}{1-N'}\frac{1-N}{N} 
\end{equation}
\\
\begin{equation}\label{eq:beta-def}
        \beta = \frac{R}{R''} = \frac{N}{1-N}\frac{1-N''}{N''} 
\end{equation}
\end{subequations}

@@

\begin{equation}
\setcounter{MaxMatrixCols}{20}
\begin{bmatrix}
     -1      & 1-\theta_{_{S+1}} & 0                 & ...  & 0            & 0            & 0             & 0             & 0             & ... & 0               & 0  & 0 \\
\theta_{_S}  & -1                & 1-\theta_{_{S+2}} & ...  & 0            & 0            & 0             & 0             & 0             & ... & 0               & 0  & 0 \\
             &                   &                   &      &              &              & ...           &               &               &     &                 &    &   \\
 0           & 0                 & 0                 & ...  & \theta_{_-2} & -1           & 1-\theta_{_0} & 0             & 0             & ... & 0               & 0  & 0 \\
 0           & 0                 & 0                 & ...  & 0            & \theta_{_-1} & -1            & 1-\theta_{_1} & 0             & ... & 0               & 0  & 0 \\
 0           & 0                 & 0                 & ...  & 0            & 0            & \theta_{_0}   & -1            & 1-\theta_{_2} & ... & 0               & 0  & 0 \\
             &                   &                   &      &              &              & ...           &               &               &     &                 &    &   \\
 0           & 0                 & 0                 & ...  & 0            & 0            & 0             & 0             & 0             & ... & \theta_{_{E-2}} & -1 & 1-\theta_{_E} \\
 0           & 0                 & 0                 & ...  & 0            & 0            & 0             & 0             & 0             & ... & 0               & \theta_{_{E-1}} & -1
 \end{bmatrix}
 \times
 \begin{bmatrix}
     F_{_{S}}   \\
     F_{_{S+1}} \\
     \cdots     \\
     F_{_{-1}}  \\
     F_{_{0} }  \\
     F_{_{1} }  \\
     \cdots     \\
     F_{_{E-1}} \\
     F_{_{E}}
 \end{bmatrix}
 =
 \begin{bmatrix}
     0      \\
     0      \\
     \cdots \\
     0      \\
     F      \\
     0      \\
     \cdots \\
     0      \\
     0
\end{bmatrix}
%\caption{caption needed!}
\label{eq:flow}
\end{equation}

@@

Little information is available about optimising an existing enrichment cascade
that is being fed with a feed enrichment that does not match the design
enrichment. So far 3 different methods have been investigated.

The first one assumes that no change are been made to the cascade, i.e $\delta
U$, $F$ and $\theta$ are fixed across all stages. The second one assumes the cut
value at each stage is retuned to maintain the ideal state of the cascade,
$\alpha$ and $\beta$ remain fixed. The last one, described in \cite{walker.2017}
assumes the tails to product enriching factor and the cut remain constants ($\gamma =
\alpha\times\beta$). Models behaviors and assumptions are summarized in Tab.
\ref{tab:models}.
